---
title: "Introduction to Network Analysis with R"
description: Here is how a basic ML algorithm classify the novel texts.
author: "Dr. Suat ATAN"
output: html_document
date: "2020-03-03 05:05:00 +0300"
tags:
- network_analysis
- learn
categories:
- R
- English
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Quick Start

Instead of theoretical explanations let's just think about this scenario. You are monitoring e-mails between these persons A, B, C, D, E, F, G, H without details of the e-mails. Just the traffic of the emails. You have this table:

|From|To|
|----|--|
|A|B|
|A|C|
|D|E|
|D|F|
|E|G|
|E|H|
|A|H|
|B|H|

We say **directed** because there is an arrow from A to B. This reflects there is a movement or directed relation like sending an e-mail or sending money or calling someone. Keep this in the mind, if there is "sending" this requires a "directed" graph. Of course, two things sometimes do not require direction in their relation. Think about friendship. There is no direction, you and your friend are just connected. This kind of relation is **undirected**.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#directed
library(igraph)
g <- graph_from_literal(A-+B)
plot(g)
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#undirected
library(igraph)
g <- graph_from_literal(A--B)
plot(g)
```


Now, let's try to show all relations. Of course, we are doing it *literally*. If you have this table you can use `graph_from_data_frame()` function. We are using `graph_from_literal()` function with a special notation. In directed graphs, edges will be created only if the edge operator includes a arrow head (‘+’) at the end of the edge:

```{r}
g <- graph_from_literal(A-+B,
                        A-+C,
                        D-+E,
                        D-+F,
                        E-+G,
                        E-+H,
                        A-+H,
                        B-+H)
plot(g)
```

To be continued