---
title: 'Market Basket Analysis'
output: html_document
author: "Dr. Suat ATAN"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(arules)
library(arulesViz)
library(tidyverse)
library(readxl)
library(knitr)
library(ggplot2)
library(lubridate)
library(plyr)
library(dplyr)

```

# Data Set

First column is *FaturaNo*. It reflects one procurement has been made by any user and products in the *Urun* column. 

```{r}
#read excel into R dataframe
retail <- read_excel('suat_market.xlsx')
head(retail)
```


# Preprocessing Data

```{r}
#complete.cases(data) will return a logical vector indicating which rows have no missing values. Then use the vector to get only rows that are complete using retail[,].
retail <- retail[complete.cases(retail), ]
glimpse(retail)
```
# Converting data from Relational Format To Transactional Format

In this format, each procurement becomes single row. This conversion is required.

```{r}
library(plyr)
#ddply(dataframe, variables_to_be_used_to_split_data_frame, function_to_be_applied)
# THIS CODE MERGES EACH INVOICE AND CONCATS THE PRODUCTS
transactionData <- ddply(retail,c("FaturaNo"),
                       function(df1)paste(df1$Urun,
                       collapse = ","))
#The R function paste() concatenates vectors to character and separated results using collapse=[any optional charcater string ]. Here ',' is used
transactionData
```


# Removing Unecessary Columns

After removal, data will be in the form of *market basket format* and can be readable by `arule`  market basket analysis library.

```{r}
colnames(transactionData) <- c("items")
transactionData$items <- NULL
transactionData
```

```{r}
write.csv(transactionData,"suatmarket_basket_transactions.csv", quote = FALSE, row.names = FALSE)
```

# Read Data in Arule Format

```{r}
tr <- read.transactions('suatmarket_basket_transactions.csv', format = 'basket', sep=',')
tr
```

# Showing Descriptive Stats

```{r}
summary(tr)
```

# Most Frequent Sales

```{r}
# Create an item frequency plot for the top 20 items
if (!require("RColorBrewer")) {
  # install color package of R
install.packages("RColorBrewer")
#include library RColorBrewer
library(RColorBrewer)
}
itemFrequencyPlot(tr,topN=20,type="absolute",col=brewer.pal(8,'Pastel2'), main="Absolute Item Frequency Plot")
```

# Generating Rules


```{r}
# Min Support as 0.001, confidence as 0.8.
association.rules <- apriori(tr, parameter = list(supp=0.001, conf=0.8,maxlen=10))
```

```{r}
summary(association.rules)
```
# Results

Let's show most clear rules. If the confidence is 1 it means "%100 of customers". For instance %100 of users buys *bal * with the *tereyagi*. 

```{r}
inspect(association.rules[1:50])
```

# Finding Rules related to given items

```{r}
bebekbezi.association.rules <- apriori(tr, parameter = list(supp=0.001, conf=0.8),appearance = list(default="lhs",rhs="bebekbezi"))
```
```{r}
inspect(bebekbezi.association.rules)
```

# Visualize

```{r}
# Filter rules with confidence greater than 0.4 or 90%
subRules<-association.rules[quality(association.rules)$confidence>0.9]
#Plot SubRules
plot(subRules)
```

```{r}
plot(subRules,method="two-key plot")
```

# Interactive

```{r}
plotly_arules(subRules)
```

# Network Analysis

```{r}
top10subRules <- head(subRules, n = 10, by = "confidence")
plot(top10subRules, method = "graph",  engine = "htmlwidget")
```

