---
title: "Introduction to Network Analysis with R"
description: Things are connected. Let's discover.
author: "Dr. Suat ATAN"
date: "2020-05-03 05:05:00 +0300"
tags:
- network_analysis
- learn
categories:
- R
- English
---


# Quick Start

Instead of theoretical explanations let's just think about this scenario. You are monitoring e-mails between these persons A, B, C, D, E, F, G, H without details of the e-mails. Just the traffic of the emails. You have this table:

|From|To|
|----|--|
|A|B|
|A|C|
|D|E|
|D|F|
|E|G|
|E|H|
|A|H|
|B|H|

We say **directed** because there is an arrow from A to B. This reflects there is a movement or directed relation like sending an e-mail or sending money or calling someone. Keep this in the mind, if there is "sending" this requires a "directed" graph. Of course, two things sometimes do not require direction in their relation. Think about friendship. There is no direction, you and your friend are just connected. This kind of relation is **undirected**.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#directed
library(igraph)
g <- graph_from_literal(A-+B)
plot(g)
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#undirected
library(igraph)
g <- graph_from_literal(A--B)
plot(g)
```


Now, let's try to show all relations. Of course, we are doing it *literally*. If you have this table you can use `graph_from_data_frame()` function. We are using `graph_from_literal()` function with a special notation. In directed graphs, edges will be created only if the edge operator includes a arrow head (‘+’) at the end of the edge:

```{r}
# the line which starts the # are comment not code
# computers isn't so smart and cannot understand us
# except lines below :)
# g is our graph object

g <- graph_from_literal(A-+B,
                        A-+C,
                        D-+E,
                        D-+F,
                        E-+G,
                        E-+H,
                        A-+H,
                        B-+H)
# we are plotting it
plot(g)
```

# Who is who? Understanding Network Metrics

OK. We have visualized our first network diagram. Before any calculation, the diagram is pretty self-explanatory.  For instance, A looks like has never received any e-mail. C and F look like just 'getter' they didn't send any e-mail. For this kind of easy network visualization simply works and maybe there is no need for any computation. However, when things are messy we should calculate the **importance** of each node. Of course, there are more metrics. But let's keep things simple and go. Are you ready? We will calculate the **degree metric** of each person (or let's remember nomenclature: node) 

```{r}
degree(g)
```

That's all. Each person has a number and each number reflects how many numbers the node has. As you know, the bigger number reflects a bigger interaction. Persons like F and G is not so "active". Let's fire them :)